FATE summary results

### 2019-12-31 paper draft.Rmd
New plankton DFA plot
Tweaks to plots

```{r, echo=F}
# all <- readRDS("all_plankton_12.11.19.one.trend.rds") 
all <- readRDS("GOA_plankton_11.18.19.one.trends.rds") 
all$summary
```

@@

plot.c <- ggplot(mod, aes(x=SST)) +
  theme_bw() +
  geom_density(fill=cb[3]) + 
  geom_hline(yintercept=0) + 
  geom_vline(xintercept = 0, lty=2) + 
  xlab("Slope") + 
  ylab("Density") +
  ggtitle(("c) Plankton slope on SST")) +
  theme(title = element_text(size=8)) +
  xlim(-3.2,0.5)

@@

>>>>

```{r, echo=F}
all <- readRDS("all_plankton_12.11.19.one.trend.rds")
# all <- readRDS("GOA_plankton_11.18.19.one.trends.rds") 
all$summary
```

@@

plot.c <- ggplot(mod, aes(x=SST)) +
  theme_bw() +
  geom_density(fill=cb[3], color=NA) + 
  geom_hline(yintercept=0) + 
  geom_vline(xintercept = 0, lty=2) + 
  xlab("Slope") + 
  ylab("Density") +
  ggtitle(("c) Plankton slope on SST")) +
  theme(title = element_text(size=8)) +
  xlim(-3.2,0.5)

@@

dev.off()
#######

plot.null <- ggplot() + theme_void()

png("combined all plankton time series plots.png", 6, 6, units="in", res=300)

ggpubr::ggarrange(ggpubr::ggarrange(plot.null,plot.a, plot.null, ncol=3, nrow=1, widths=c(0.1, 1, 0.2)),
                  ggpubr::ggarrange(plot.b, plot.c, ncol=2, widths=c(1.5, 0.8), nrow=1),
                  nrow=2, heights=c(1, 0.8))
